---
title: "QMM_ASSIGNMENT2"
author: "Yeswanth Siripurapu"
date: "2023-10-02"
output:
  pdf_document: default
  html_document: default
---

#This notebook contains the code for Assignment The Transportation Model

#Summary:
#1.Object: *The LP model is used to estimate an optimal total cost, which 
#represents the lowest cost the linear program with 20 decision variables and
#9 constraints 
#One of the limitations in month 1 is actually around ten engines which Northern
#Aeroplane Company may encounter when fulfilling contractual responsibilities.
#This indicates that just 10 units are produced on a minimum cumulative basis in
#month.
#1. An accumulation of output to satisfy constraint number two, a requirement of
#25 engines must be met in month.
#2. This restriction establishes a minimum50 engines must be produced overall in
#month 3 as a requirement. This restriction calls for the bare minimal.The total
#number of engines produced in month four will be 70.
#2.Sensitivity Analysis for the Objective Function: * Using the sensitivity 
#analysis, we can determine how changes in the price of production and storage 
#will affect the overall cost. Making educated decisionsregarding costmanagement
#will be made easier if you experiment with production cost coefficients and 
#monthly storage charges to see how they effect minimum total cost.
#3. LP offers a manufacturing and storage strategy that is cost-effective and
#satisfies contractual requirements. A sensitivity analysis demonstrates how 
#modifications to important variables affect the expenses related to varying 
#production levels. Shadow pricing offer information on the effects of changing 
#production levels.
#More detailson the sensitivity ofthe objective function to changes in objective
#coefficients are revealed by reduced costs. Northern Aeroplane Company has the
#capacity to strategic decisions regarding engineproduction and storage based on
#this information.

#Load lpSolveAPI

```{r}
library(lpSolveAPI)
```

#Problem Statement: The NORTHERN AIRPLANE COMPANY builds commercial airplanes 
#for various airline companies around the world.The last stage in the production
#process is to produce the jetengines and then to install them a very fast
#operation in the completed airplane frame. The company has been working
#under some contracts to deliver a considerable number of airplanes in the near 
#future, and the production of the jet engines for these planes must now be 
#scheduled for the next four months. To meet the contracted dates for delivery,
#the company must supply engines for installation in the  quantities indicated 
#in the second column of Table 9.7. Thus, the cumulative number of engines 
#produced by the end of months 1, 2, 3, and 4 must be at least 10, 25, 50,and 70
#respectively. The facilities that will be available for producing the
#engines vary according to other production, maintenance, and renovation work
#scheduled during this period.The resulting monthly differences in the maximum
#number that can be produced and the cost (in millions of dollars) of producing 
#each one are given in the third and fourth columns of Table 9.7 
#Because of the variations in production costs, it may well be worthwhile to 
#produce some of the engines a month or more before they are scheduled for 
#installation, and this possibility is being considered. The drawback is that 
#such engines must be stored until the scheduled installation (the airplane
#frames will not 1 be ready early) at a storage cost of $15,000 permonth foreach
#engine,1 as shown in the rightmost column of Table 9.7.The production manager
#wants a schedule developed for the number of engines to be produced in each of
#the four months so that total of the production& storage costs will be minimized.
#Formulate and solve this problem. Submit a final pdf knitted file with your 
#recommendations


#We now read the lp formulation using an lp file. To read about about the lp format for files, you can readthe documentation at http://lpsolve.sourceforge.net/5.5/lp-format.html

```{r}

x<-read.lp("Northern Airplane Co.lp")
x
```
#Solve the lp model

```{r}
solve(x)
```
# get objective value

```{r}
get.objective(x)
```
#get shadow prices

```{r}
get.sensitivity.rhs(x) 
```

# get constraint RHS values
```{r}
get.constraints(x) 

```

#get values of decision variables

```{r}
get.variables(x)

```

# Retrieve the sensitivity of the objective function
```{r}
get.sensitivity.objex(x)

```

# get reduced cost

```{r}
get.sensitivity.obj(x)

```






